\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage[belowskip=-13pt,aboveskip=4pt]{caption}
\captionsetup[table]{skip=0pt}
%\setlength{\belowcaptionskip}{-10pt}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%MAYBE set this
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA}
%\acmYear{1997}
%\copyrightyear{2016}

\acmConference{CS395T: Datacenters}{Fall 2018}{University of Texas at Austin}
%\acmYear{1997}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}


\begin{document}
\title{Linux-Integrated TCP Acceleration as a Service}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Amanda Austin}
\affiliation{
  \institution{University of Texas at Austin}
}
%\email{jsmith@affiliation.org}

\author{Henrique Fingler}
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{
  \institution{University of Texas at Austin}
}
%\email{trovato@corporation.com}


\author{Timothy Stamler}
\affiliation{
  \institution{University of Texas at Austin}
}
%\email{jsmith@affiliation.org}

% The default list of authors is too long for headers.
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}
Networking speeds have increased while CPU speeds have not. As a result, an
increasing portion of packet processing time is spent in the kernel
networking stack. To mitigate this effect, TCP Acceleration as a Service
(TAS) was presented as a solution for efficient, predictable, highly scalable
TCP packet processing. TAS splits TCP processing into a fast path and a slow 
path, both of which operate as userspace processes. In doing so, however, TAS 
loses some information about the network when compared to an in-kernel 
networking stack (e.g., firewalls, ARP tables). We present a Linux-integrated 
TAS that interfaces with Linux via a virtual network device. TAS duplicates some
slow path packets to Linux via this virtual device, observes Linux's response,
and then mimics that response. We show that this method can allow TAS to use
Linux's information about the network while retaining the performance of TAS
fast path operations.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
%\begin{CCSXML}
%<ccs2012>
% <concept>
%  <concept_id>10010520.10010553.10010562</concept_id>
%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%  <concept_significance>500</concept_significance>
% </concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}


%\keywords{ACM proceedings, \LaTeX, text tagging}

\maketitle


\input{sections/intro}

\input{sections/background}

\input{sections/design}

\input{sections/implementation}

\input{sections/eval}

\input{sections/future}

\input{sections/conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}
